---
title: "Cata Botsi: Student arrivals"
author: "David Jackson"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(scales)
```

```{r}
rm(list=ls())
df <- read.delim("./transactions.csv",sep="|")
df <- df %>% select(-X,-X.1)
# df$Ymd <- as.Date(df$Date,format ="%m/%d/%Y")
summary(df$Duration)
```

#### (1) What distribution best describes the transaction duration for the entire data set?

* Answer: Uniform distribution

```{r}
hist(df$Duration,  main = "Uniform Distribution: Duration ")
```

#### (3) Calculate the 99% confidence limits for the mean of the transaction duration of the entire data set. Round
your answers to three decimal places. For example, 1.234. 

* Lower limit: 6.005
* upper limit: 6. 090

```{r}
boxplot(df$Duration)
t.test(df$Duration,conf.level = 0.99)
```

#### (4) You read a discussion on the third year WhatsApp group where a student claims the answer to question 2. was a uniform distribution. Do you believe the claim?  Yes or  No

* Yes it is a uniform distribution

```{r}


```

